Comparison of three similarity scores for bullet LEA matching

### 2019-12-24 index.Rnw
Required documents for upload

h44nest <- h44nest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  }),
  sam_cms = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$cms)
    max(scores)
  })
)
h44nest <- h44nest %>%
  mutate(
    barrel2 = factor(barrel2, levels = c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels = rev(c(
      "K", "O", "L", "P",
      "J",
      "H", "I", "Y", "G",
      "E", "U", "X", "F",
      "T", "S"
    ))),
    bullet2 = factor(bullet2, levels = c(1:2, rev(levels(bullet1))))
  )
h44 <- h44nest %>%
  ggplot(aes(
    y = bullet1, x = bullet2,
    fill = sam_rf
  )) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, space = "free", scales = "free") +
  ylab("Questioned bullets") +
  xlab("Test fires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.35, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +

@@

pdnest <- pdnest %>%
  mutate(
    bullet2 = factor(bullet2, levels = rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z"))),
    bullet1 = factor(bullet1, levels = c("B1", "B2", "B3", rev(levels(bullet2))))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel1, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.45, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +
  scale_y_discrete() +
  theme_bw() +
  theme(legend.position = "bottom") +
  #  coord_equal() +
  geom_tile(aes(colour = TRUE),
    size = .5,
    data = filter(pdnest, KM)
  ) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))

@@

hou1nest <- hounest %>%
  filter(group1 == "G1") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U40", "U36", "U42", "U10", "U77", "U37", "U28", "U15"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

@@

hou2nest <- hounest %>%
  filter(group1 == "G2") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U23", "U41", "U61", "U98", "U73", "U34", "U63", "U66"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )
hou2 <- hou2nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.375, limits = c(0, 1)
  ) +
  scale_y_discrete() +
  scale_colour_manual("same source", values = "darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou2nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 2")

hou3nest <- hounest %>%
  filter(group1 == "G3") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U27", "U33", "U36", "U49", "U56", "U65", "U14", "U45"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

@@

<<compare, fig.width = 8, fig.height = 7, fig.cap="Density curves of similarity scores from random forest scores (top), cross correlation (middle), and consecutive matching striae (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs.">>=
nests <- rbind(
  h44nest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Hamby 44", group1 = NA),
  pdnest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Phoenix PD", group1 = NA),
  hounest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key = "measure", value = "value", sam_rf, sam_ccf, sam_cms)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross correlation", "CMS", "RF score")

@@

all_lands <- rbind(
  h44lands %>%
    select(rfscore, ccf, cms, sameland, samesource) %>%
    mutate(study = "Hamby 44", group1 = ""),
  pdlands %>%
    select(rfscore, ccf, cms, sameland, samesource) %>%
    mutate(study = "Phoenix PD", group1 = ""),
  houlands %>%
    select(rfscore, ccf, cms, sameland, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
all_lands$study <- factor(all_lands$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
all_lands <- all_lands %>%
  mutate(
    sameland = replace(sameland, !samesource, FALSE)
  )
@

@@

<<output-all-figs, include = F>>=
thisdoc <- readLines("index.Rmd")

# First, get figures that aren't in code chunks
# Haven't really tested this part - regex may need work
raw_figures <- data_frame(
  line_start = which(str_detect(thisdoc, "\\begin\\{figure\\}")), 
  line_end = which(str_detect(thisdoc, "\\end\\{figure\\}")),
  subfloats = purrr::map2(line_start, line_end, 
                          ~str_extract(thisdoc[.x:.y], "\\includegraphics(?:\\[.*\\])?\\{(.*)\\}") %>%
                            str_replace("\\includegraphics(?:\\[.*\\])?\\{(.*)\\}", "\\1"))
)

# Code chunk figures
chunk_figures <- data_frame(
  line_start = which(str_detect(thisdoc, "^```\\{r.*\\}$")),
  line_end = which(str_detect(thisdoc, "^``` *$")),
  chunk_name = str_replace(thisdoc[line_start], "(```\\{r ?)([0-9A-z-]*)(,?.*\\})", "\\2")
) %>% 
  mutate(
    chunk_name = ifelse(chunk_name == "", "unnamed-chunk", chunk_name),
  ) %>% 
  mutate(
    subfloats = purrr::map2(line_start, chunk_name, ~thisdoc[.x] %>%
                              str_extract("fig\\.subcap ?= ?.*?\\),") %>%
                              str_replace("fig\\.subcap ?= ?", "") %>%
                              str_replace(",$", "") %>%
                              parse(text=.) %>% eval %>% length() %>% 
                              seq(1, ., by = 1) %>%
                              sprintf("figures/%s-%d.pdf", .y, .))
  )

# Knitr included graphics figures
chunk_incl_figures <- data_frame(
  line_start = which(str_detect(thisdoc, "^```\\{r.*\\}$")),
  line_end = which(str_detect(thisdoc, "^``` *$")),
  chunk_name = str_replace(thisdoc[line_start], "(```\\{r ?)([0-9A-z-]*)(,?.*\\})", "\\2")
) %>% 
  mutate(
    chunk_name = ifelse(chunk_name == "", "unnamed-chunk", chunk_name),
  ) %>% 
  mutate(
    subfloats = purrr::map2(line_start, line_end, function(.x, .y) {
      thisdoc[.x:.y] %>%
        paste(collapse = " ") %>%
        str_extract(., "include_graphics\\(c?\\(?.*?\\)?\\)") %>%
        str_replace("include_graphics\\(", "") %>%
        str_extract_all('\\"[\\.A-z0-9 /-]*?\\"') %>%
        parse(text = .) %>% eval() %>%
        str_remove_all("\\\\|\"")
    })
  )

# All figures
figs <- bind_rows(raw_figures, chunk_figures, chunk_incl_figures) %>%
  arrange(line_start) %>%
  mutate(subfloats = purrr::map(subfloats, function(x) data_frame(file = x, exists = file.exists(x)))) %>%
  tidyr::unnest() %>%
  filter(exists) %>%
  mutate(fig_num = group_indices(., line_start, line_end)) %>%
  group_by(fig_num) %>%
  mutate(rn = 1:n(),
         maxrn = n(),
         fig_label = letters[rn],
         fig_label = ifelse(maxrn > 1, fig_label, ""),
         fileext = tools::file_ext(file),
         fig_label = sprintf("Figure_%d%s.%s", fig_num, fig_label, fileext))

>>>>

h44nest <- h44nest %>% mutate(
  sam_ccf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  }),
  sam_cms = data %>% purrr::map_dbl(.f = function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$cms)
    max(scores)
  })
)
h44nest <- h44nest %>%ungroup() %>% 
  mutate(
    barrel2 = factor(barrel2, levels = c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels = rev(c(
      "K", "O", "L", "P",
      "J",
      "H", "I", "Y", "G",
      "E", "U", "X", "F",
      "T", "S"
    ))),
    bullet2 = factor(bullet2, levels = c(1:2, rev(levels(bullet1))))
  )
h44 <- h44nest %>%
  ggplot(aes(
    y = bullet1, x = bullet2,
    fill = sam_rf
  )) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, space = "free", scales = "free") +
  ylab("Questioned bullets") +
  xlab("Test fires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.35, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +

@@

pdnest <- pdnest %>%ungroup() %>% 
  mutate(
    bullet2 = factor(bullet2, levels = rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z"))),
    bullet1 = factor(bullet1, levels = c("B1", "B2", "B3", rev(levels(bullet2))))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel1, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.45, limits = c(0, 1)
  ) +
  scale_colour_manual("same source", values = "darkorange") +
  scale_y_discrete() +
  theme_bw() +
  theme(legend.position = "bottom") +
  #  coord_equal() +
  geom_tile(aes(colour = TRUE),
    size = .5,
    data = filter(pdnest, KM)
  ) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))

@@

hou1nest <- hounest %>%ungroup() %>% 
  filter(group1 == "G1") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U40", "U36", "U42", "U10", "U77", "U37", "U28", "U15"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

@@

hou2nest <- hounest %>%ungroup() %>% 
  filter(group1 == "G2") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U23", "U41", "U61", "U98", "U73", "U34", "U63", "U66"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )
hou2 <- hou2nest %>%
  ggplot(aes(y = bullet1, x = bullet2, fill = sam_rf)) +
  geom_tile(size = 1) +
  facet_grid(. ~ barrel2, scales = "free", space = "free") +
  ylab("Questioned bullets") +
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ",
    low = "darkgrey",
    high = "darkorange", midpoint = 0.375, limits = c(0, 1)
  ) +
  scale_y_discrete() +
  scale_colour_manual("same source", values = "darkorange") +
  geom_tile(aes(colour = TRUE), size = .5, data = filter(hou2nest, sam_rf > 0.3)) +
  guides(colour = guide_legend(override.aes = list(fill = NA))) + ggtitle("Houston set 2")

hou3nest <- hounest %>%ungroup() %>% 
  filter(group1 == "G3") %>%
  mutate(
    bullet1 = factor(bullet1, levels = rev(c("U27", "U33", "U36", "U49", "U56", "U65", "U14", "U45"))),
    bullet2 = factor(bullet2, levels = c("B1", "B2", "B3", levels(bullet1)))
  )

@@

<<compare, fig.width = 8, fig.height = 7, fig.cap="Density curves of similarity scores from random forest scores (top), cross correlation (middle), and consecutive matching striae (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs.">>=
nests <- rbind(
  h44nest %>%ungroup() %>% 
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Hamby 44", group1 = NA),
  pdnest %>%ungroup() %>% 
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Phoenix PD", group1 = NA),
  hounest %>%ungroup() %>% 
    select(sam_rf, sam_ccf, sam_cms, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key = "measure", value = "value", sam_rf, sam_ccf, sam_cms)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross correlation", "CMS", "RF score")

@@

all_lands <- bind_rows(
  h44lands %>%
    select(rfscore, ccf, cms, sameland, samesource) %>%
    mutate(study = "Hamby 44", group1 = ""),
  pdlands %>%
    select(rfscore, ccf, cms, sameland, samesource) %>%
    mutate(study = "Phoenix PD", group1 = ""),
  houlands %>%
    select(rfscore, ccf, cms, sameland, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
all_lands$study <- factor(all_lands$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
all_lands <- all_lands %>%
  mutate(
    sameland = replace(sameland, !samesource, FALSE)
  )
@

@@

<<output-all-figs, eval = F, include = F>>=
thisdoc <- readLines("index.Rnw")

# First, get figures that aren't in code chunks
# Haven't really tested this part - regex may need work
raw_figures <- tibble(
  line_start = which(str_detect(thisdoc, "\\begin\\{figure\\}")), 
  line_end = which(str_detect(thisdoc, "\\end\\{figure\\}")),
  subfloats = purrr::map2(line_start, line_end, 
                          ~str_extract(thisdoc[.x:.y], "\\includegraphics(?:\\[.*\\])?\\{(.*)\\}") %>%
                            str_replace("\\includegraphics(?:\\[.*\\])?\\{(.*)\\}", "\\1"))
)

# Code chunk figures
chunk_figures <- tibble(
  line_start = which(str_detect(thisdoc, "^<<.*>>=$")),
  line_end = which(str_detect(thisdoc, "^@$")),
  chunk_name = str_replace(thisdoc[line_start], "<<([0-9A-z-]*?),?((?:.*=.*){1,})>>=", "\\1")
) %>% 
  mutate(
    chunk_name = ifelse(chunk_name == "", "unnamed-chunk", chunk_name),
  ) %>% 
  mutate(
    subfloats = purrr::map2(line_start, chunk_name, ~thisdoc[.x] %>%
                              str_extract("fig\\.subcap ?= ?.*?\\),") %>%
                              str_replace("fig\\.subcap ?= ?", "") %>%
                              str_replace(",$", "") %>%
                              parse(text=.) %>% eval %>% length() %>% 
                              seq(1, ., by = 1) %>%
                              sprintf("figures/%s-%d.pdf", .y, .))
  )

# Knitr included graphics figures
chunk_incl_figures <- tibble(
  line_start = which(str_detect(thisdoc, "^<<.*>>=$")),
  line_end = which(str_detect(thisdoc, "^@$")),
  chunk_name = str_replace(thisdoc[line_start], "<<([0-9A-z-]*?),?((?:.*=.*){1,})>>=", "\\1")
) %>% 
  mutate(
    chunk_name = ifelse(chunk_name == "", "unnamed-chunk", chunk_name),
  ) %>% 
  mutate(
    subfloats = purrr::map2(line_start, line_end, function(.x, .y) {
      thisdoc[.x:.y] %>%
        paste(collapse = " ") %>%
        str_extract(., "include_graphics\\(c?\\(?.*?\\)?\\)") %>%
        str_replace("include_graphics\\(", "") %>%
        str_extract_all('\\"[\\.A-z0-9 /-]*?\\"') %>%
        parse(text = .) %>% eval() %>%
        str_remove_all("\\\\|\"")
    })
  )

# All figures
figs <- bind_rows(raw_figures, chunk_figures, chunk_incl_figures) %>%
  arrange(line_start) %>%
  mutate(subfloats = purrr::map(subfloats, function(x) data_frame(file = x, exists = file.exists(x)))) %>%
  tidyr::unnest() %>%
  filter(exists) %>%
  mutate(fig_num = group_indices(., line_start, line_end)) %>%
  group_by(fig_num) %>%
  mutate(rn = row_number(),
         maxrn = n(),
         fig_label = letters[rn],
         fig_label = ifelse(maxrn > 1, fig_label, ""),
         fileext = tools::file_ext(file),
         fig_label = sprintf("Figure_%d%s.%s", fig_num, fig_label, fileext))

### 2019-12-24 title_page.tex
Required documents for upload

\documentclass[titlepage]{article}
\title{Case study validations of automatic bullet matching}
\author{Susan Vanderplas and Heike Hofmann}
\date{Center for Statistics and Applications in Forensic Evidence, Iowa State University. 195 Durham Center, 613 Morill Rd., Ames, IA 50011}

>>>>

\documentclass{article}
\usepackage{fullpage}

\title{Comparison of three similarity scores for bullet LEA matching}
\author{Susan Vanderplas$^\ast$$^{1,2}$, Melissa Nally$^3$, Tylor Klep$^4$, Cristina Cadevall$^5$, Heike Hofmann$^1$}

\date{$^\ast$ Corresponding author. email: susan.vanderplas@unl.edu\\[1em]
$^1$Center for Statistics and Applications in Forensic Evidence, Iowa State University\\
195 Durham Center, 613 Morill Rd., Ames, IA 50011\\[1em]
$^2$Statistics Department, University of Nebraska Lincoln\\340 Hardin Hall North Wing, Lincoln, NE 68583-0963\\[1em]
$^2$Houston Forensic Science Center\\500 Jefferson St 13th Floor, Houston, TX 77002\\[1em]
$^3$Phoenix Police Department\\Laboratory Services Bureau\\621 W Washington St, Phoenix, AZ 85003\\[1em]
$^4$Sensofar Group\\Parc Audiovisual de Catalunya Ctra, BV-1274, Km 1, 08225 Terrassa, Barcelona, Spain}
